Exploring the ``Party City'' effect in the NBA

### 2017-07-04 legacy/eda_report.rnw
Moved legacy code.

\subsection*{Motivation}
It's not unreasonable to think that game performance can be affected (in part) by what takes place off the basketball court. We are interested to see if teams exhibit a decline in performance the day following a game in a party city. We exploit data on bookmaker spreads: the expected score differential between two teams after conditioning on observable performance. We expect a team to meet the spread half the time; if not, the bookmakers would open up an opportunity for arbitrage over the long-term. We construct a model which attempts to estimate the causal effect of  visiting a ``party-city'' the day before a game on the probability of meeting the spread.

@@

\subsection*{Which teams to include as party cities?}
<<echo=-1>>=

@@

summary(model)$coef[c(1:6, sample(7:nrow(coef(summary(model))), size = 6)), ]
@

>>>>

@@

\section{Motivation}
It's not unreasonable to think that game performance can be affected (in part) by what takes place off the basketball court. We are interested to see if teams exhibit a decline in performance the day following a game in a party city. We exploit data on bookmaker spreads: the expected score differential between two teams after conditioning on observable performance. We expect a team to meet the spread half the time; if not, the bookmakers would open up an opportunity for arbitrage over the long-term. We construct a model which attempts to estimate the causal effect of  visiting a ``party-city'' the day before a game on the probability of meeting the spread.

\section{Which teams to include as party cities?}

<<echo=-1>>=

@@

summary(model)
@
